Let’s Disco – Publishing person-level data as Linked Data.

### 2015-01-09 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
typos

Another objective of the tutorial is to share our experience in developing a RDF vocabulary out of an existing and highly-complex domain-specific data model. We provide insight into the development and engineering process for creating Disco.
Finally, since Disco is already being adopted in the DDI community, we aim to increase the use of Disco in the Linked Data community.

>>>>

Another objective of the tutorial is to share our experience in developing an RDF vocabulary out of an existing and highly-complex domain-specific data model. We provide insight into the development and engineering process for creating Disco.
Finally, since Disco is already being adopted in the DDI community, we aim to increase the use of Disco in the Linked Data community.
